Critical Temperature of the Ising Ferromagnet on Proximity Graphs derived from Square Lattices by Site Displacement

### 2016-03-14 Tex/paper.tex
truncated precision in table
tweaks to diagrams

                    RNG          & 0.0 & 2.2688(7) & 1.00(1) & 1.741(2) & 0.125(1) \\
                                 & 0.1 & 2.2053(6) & 0.99(1) & 1.745(5) & 0.128(3) \\
                                 & 0.2 & 1.6265(19)& 1.02(2) & 1.758(14)& 0.122(7)\\
                                 & 0.5 & 1.2825(9) & 1.01(2) & 1.746(16)& 0.128(8)\\
                                 & 1.0 & 1.2125(5) & 1.01(1) & 1.764(14)& 0.125(6)\\

@@

                    GG           & 0.0 & 2.2688(6) & 1.00(1) & 1.738(22)& 0.127(4)\\
                                 & 0.1 & 2.8944(43)& 1.00(1) & 1.745(6) & 0.135(6) \\
                                 & 0.3 & 2.5281(27)& 1.03(3) & 1.718(15)& 0.118(11)\\
                                 & 0.5 & 2.2388(9) & 1.01(1) & 1.747(12)& 0.125(11)\\
                                 & 1.0 & 2.1275(20)& 1.04(3) & 1.750(16)& 0.125(15)\\

@@

        This study examines the critical temperatures $T_c$ for different values of $\sigma$.
        Therefore the knowledge that the Binder cumulants $g$ for different
        system sizes $L$ intersect at $T_c$ \cite{Binder1981} as shown in Fig.~\ref{sfig:Tc:binder}
        is used.
        \begin{figure*}[hbtp]
            \subfigure[]{
                \label{sfig:Tc:binder}
                \includegraphics[scale=1]{plots/binder}
            }
            \subfigure[]{
                \label{sfig:Tc:RNG}
                \label{sfig:Tc:GG}
                \includegraphics[scale=1]{plots/Tc_both}
            }
            \subfigure[]{
                \label{fig:TcK}
                \includegraphics[scale=1]{plots/K_sigma_inset_both}
            }
            \caption[Critical Temperature over Different Disorder Parameters]
            {
                \subref{sfig:Tc:binder} Critical temperatures \(T_c\) are obtained by finding the intersections
                of the Binder parameters $g$ for different system sizes $L$.
                \subref{sfig:Tc:RNG} They are plotted over different disorder parameters \(\sigma\).
                Interesting points are the jump and rise of the GG at small
                \(\sigma\) and the plateau on the RNG for small \(\sigma\).
                \subref{fig:TcK} The average degree \(K\) is plotted over $\sigma$ and
                the similarity to \subref{sfig:Tc:RNG} shows that the degree is the single
                most important influence on $T_c$. The inset shows that for the GG there
                is actually in good approximation a power-law relationship \(T_c = aK^b\)
                The upper curve is for an ensemble where the edges have unit weight and
                yields an exponent $b_1=1.321(1)$ with $\chi_{\mathrm{red}}^2 = 2.5$.
                The ensemble with length dependent weigth is the lower curve with
                $b = 1.305(2)$, $\chi_{\mathrm{red}}^2 = 4.9$.
                The bad $\chi_\mathrm{red}^2$ are caused by the region in the upper right,
                where $T_c$ is rising with $\sigma$ and hint at other influences.
            }
            \label{fig:Tc}
        \end{figure*}
        Since \(g\) is only measured for discrete values of \(T\),
        the points have to be interpolated to find the intersection. Therefore
        a \emph{cubic spline} \cite{press2007numerical} interpolation %footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
        is calculated for the measured points.
        %~ Cubic spline interpolation is a piece-wise fitting of polynoms of
        %~ degree three which are joined under the condition to be at least two
        %~ times continuously differentiable.
        %~ This interpolation type has the
        %~ advantage that it is only influenced by local points so that the
        %~ plateaus at low and high \(T\) do not influence the interpolation in
        %~ the vicinity of \(T_c\) -- in contrast to, e.g.\ an polynom fit of
        %~ degree 4, which has to be restricted to the vincinity of \(T_c\) to
        %~ yield meaningful results.
        An even better method would be the
        \emph{multiple histogram} method \cite[p. 219ff]{NewmanBarkema1999}.
        But the simple cubic spline interpolation seems to deliver results that
        are good enough, because the temperatures of the measurements are
        sufficiently near to each other. Also a cubic spline interpolation is
        far easier to obtain.

>>>>

                    RNG          & 0.0 & 2.2688(7) & 1.00(1) & 1.74(1) & 0.125(1) \\
                                 & 0.1 & 2.2053(6) & 0.99(1) & 1.75(1) & 0.128(3) \\
                                 & 0.2 & 1.6265(19)& 1.02(2) & 1.76(1) & 0.122(7)\\
                                 & 0.5 & 1.2825(9) & 1.01(2) & 1.75(2) & 0.128(8)\\
                                 & 1.0 & 1.2125(5) & 1.01(1) & 1.76(1) & 0.125(6)\\

@@

                    GG           & 0.0 & 2.2688(6) & 1.00(1) & 1.74(2) & 0.127(4)\\
                                 & 0.1 & 2.8944(43)& 1.00(1) & 1.75(1) & 0.135(6) \\
                                 & 0.3 & 2.5281(27)& 1.03(3) & 1.72(2) & 0.118(11)\\
                                 & 0.5 & 2.2388(9) & 1.01(1) & 1.75(1) & 0.125(11)\\
                                 & 1.0 & 2.1275(20)& 1.04(3) & 1.75(2) & 0.125(15)\\

@@

        This study examines the critical temperatures $T_c$ for different values of $\sigma$.
        Therefore the knowledge that the Binder cumulants $g$ for different
        system sizes $L$ intersect at $T_c$ \cite{Binder1981} as shown in Fig.~\ref{sfig:Tc:binder}
        is used.
        \begin{figure*}[hbtp]
            \subfigure[]{
                \label{sfig:Tc:binder}
                \includegraphics[scale=1]{plots/binder}
            }
            \subfigure[]{
                \label{sfig:Tc:RNG}
                \label{sfig:Tc:GG}
                \includegraphics[scale=1]{plots/Tc_both}
            }
            \subfigure[]{
                \label{fig:TcK}
                \includegraphics[scale=1]{plots/K_sigma_inset_both}
            }
            \caption[Critical Temperature over Different Disorder Parameters]
            {
                \subref{sfig:Tc:binder} Critical temperatures \(T_c\) are obtained by finding the intersections
                of the Binder parameters $g$ for different system sizes $L$.
                \subref{sfig:Tc:RNG} They are plotted over different disorder parameters \(\sigma\).
                Interesting points are the jump and rise of the GG at small
                \(\sigma\) and the plateau on the RNG for small \(\sigma\).
                \subref{fig:TcK} The average degree \(K\) is plotted over $\sigma$ and
                the similarity to \subref{sfig:Tc:RNG} shows that the degree is the single
                most important influence on $T_c$. The inset shows that for the GG there
                is actually in good approximation a power-law relationship \(T_c = aK^b\).
                The upper curve is for an ensemble where the edges have unit weight and
                yields an exponent $b_1=1.321(1)$ with $\chi_{\mathrm{red}}^2 = 2.5$.
                The ensemble with length dependent weigth is the lower curve with
                $b = 1.305(2)$, $\chi_{\mathrm{red}}^2 = 4.9$.
                The bad $\chi_\mathrm{red}^2$ are caused by the region in the upper right,
                where $T_c$ is rising with $\sigma$ and hint at other influences.
            }
            \label{fig:Tc}
        \end{figure*}
        Since \(g\) is only measured for discrete values of \(T\),
        the points have to be interpolated to find the intersection. Therefore
        a \emph{cubic spline} \cite{press2007numerical} interpolation %footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
        is calculated for the measured points.
        %~ Cubic spline interpolation is a piece-wise fitting of polynoms of
        %~ degree three which are joined under the condition to be at least two
        %~ times continuously differentiable.
        %~ This interpolation type has the
        %~ advantage that it is only influenced by local points so that the
        %~ plateaus at low and high \(T\) do not influence the interpolation in
        %~ the vicinity of \(T_c\) -- in contrast to, e.g.\ an polynom fit of
        %~ degree 4, which has to be restricted to the vincinity of \(T_c\) to
        %~ yield meaningful results.
        An even better method would be the
        \emph{multiple histogram} method \cite[p. 219ff]{NewmanBarkema1999}.
        But the simple cubic spline interpolation seems to deliver results that
        are good enough, because the temperatures of the measurements are
        sufficiently near to each other. Also a cubic spline interpolation is
        far easier to obtain.
